Graph-based Neuron Agglomeration using 3D Skeletons

### 2017-11-06 papers/cvpr2018/1_related_work.tex
Added overview of existing methods figure

>>>>

\begin{figure*}[!ht]
	\centering
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/image.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/affinities.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/watershed.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/neuroproof.png}
	\caption{An overview of the existing methods. On the left is the original EM image data. A neural network (here VD2D3D) predicts the affinities between neighboring voxels. The Zwatershed algorithm clusters these voxels into supervoxels. NeuroProof agglomerates these supervoxels to create larger segments.}
	\label{fig:pipeline}
\end{figure*}
